Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2021-10-20 src/ms.tex
updating to try to get consistency with tutorial

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/SFH_vs_fb.png}
    \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of Z/Z$_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations. The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in FIRE as a red histogram. The amount of stellar mass formed with super-solar metallicities dominates the distribution. Note that the primary axis shows $f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of mass formed in log-scale. The opposing trends of these two distributions compete throughout this study.}
    \label{fig:SFH_vs_fb}
\end{figure}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/form_eff.png}
    \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic. Each panel shows the formation efficiency for a given DWD type. The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction. The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$. The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of 2-5 for model F50. See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
    \label{fig:form_eff}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/CEsep.png}
    \caption{Interaction separation, $a_{\rm{RLO}}$, of progenitors of close DWDs across metallicity for each DWD type from model FZ. Solid lines show the average separation at the first RLO for binaries in each metallicity bin. The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin. The average interaction separation increases with metallicity for every DWD type. The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.} 
    \label{fig:CEsep}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/lisa_nums.png}
    \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value. The solid line shows the FZ population with a metallicity-dependent binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5. The LISA population of DWDs is dominated by stars with super-solar metallicities. This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$. There is a double peak in the He + He population; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
    \label{fig:lisa_nums}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=1\columnwidth]{figures/PSD.png}
    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50. The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue. The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see \ref{sec:LISA_obs} for a discussion). A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$. This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.}
    \label{fig:PSD}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/LISA_SNR_FZ.png}
	\includegraphics[width=\textwidth]{figures/LISA_SNR_F50.png}
    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model FZ and the bottom row shows the population from model F50. In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey. We find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strenght of the confusion foreground.}
    \label{fig:LISA_SNR}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{plots/Mc_vs_dist.png}
    \caption{The chirp mass vs distance for each DWD type is shown. Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude. Each panel shows one DWD type, summed over all metallicities. Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
    \label{fig:Mc_vs_dist}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=0.45\textwidth]{figures/model_comp.png}
    \caption{The top panel shows the Galactic DWD confusion fit vs GW frequency for different binary evolution assumption variations (colors) with submodel F50 shown in dashed lines and submodel FZ shown in solid lines. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for submodel FZ to submodel F50 vs to number of DWDs orbiting in the LISA band for submodel F50 only. While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ submodels within each variation exhibit a constant reduction by a factor of two compared with the F50 submodels.}
    \label{fig:model_comp}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/SFH_vs_fb.pdf}
    \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of Z/Z$_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations. The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in FIRE as a red histogram. The amount of stellar mass formed with super-solar metallicities dominates the distribution. Note that the primary axis shows $f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of mass formed in log-scale. The opposing trends of these two distributions compete throughout this study.}
    \label{fig:SFH_vs_fb}
\end{figure}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/form_eff.pdf}
    \caption{The DWD formation efficiency vs metallicity of DWD populations simulated with \cosmic. Each panel shows the formation efficiency for a given DWD type. The solid lines indicate the formation efficiency for model FZ which incorporates a metallicity-dependent binary fraction. The dashed lines indicate the formation efficiency for model F50, which assumes a constant binary fraction of $50\%$. The DWD formation efficiency drops by a factor of $4-5$ for model FZ and a factor of 2-5 for model F50. See Section~\ref{sec:formeff} for a careful description of the trends for each DWD type.}
    \label{fig:form_eff}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
    \caption{Interaction separation, $a_{\rm{RLO}}$, of progenitors of close DWDs across metallicity for each DWD type from model FZ. Solid lines show the average separation at the first RLO for binaries in each metallicity bin. The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin. The average interaction separation increases with metallicity for every DWD type. The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts.} 
    \label{fig:CEsep}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
    \caption{The number of LISA-band systems formed for each DWD type as a function of the base-10 logarithm of metallicity, normalized to solar value. The solid line shows the FZ population with a metallicity-dependent binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5. The LISA population of DWDs is dominated by stars with super-solar metallicities. This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond Z$\simeq$Z$_\odot$. There is a double peak in the He + He population; the first peak is caused by the sharp drop in formation efficiency past Z$\simeq$0.1$Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
    \label{fig:lisa_nums}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=1\columnwidth]{figures/PSD.pdf}
    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50. The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue. The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see \ref{sec:LISA_obs} for a discussion). A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$. This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz.}
    \label{fig:PSD}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/LISA_SNR_FZ.pdf}
	\includegraphics[width=\textwidth]{figures/LISA_SNR_F50.pdf}
    \caption{The ASD vs GW frequency for DWDs resolved with SNR $> 7$ for each DWD type where the top row shows the population from model FZ and the bottom row shows the population from model F50. In each panel, the LISA sensitivity curve, including the confusion foreground for each model, is shown in black and the total population for each model is shown in grey. We find that each model qualitatively exhibits similar characteristics and that the only change is in the yield of resolved DWDs for each type based on the strenght of the confusion foreground.}
    \label{fig:LISA_SNR}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/Mc_vs_dist.pdf}
    \caption{The chirp mass vs distance for each DWD type is shown. Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude. Each panel shows one DWD type, summed over all metallicities. Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
    \label{fig:Mc_vs_dist}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=0.45\textwidth]{figures/model_comp.pdf}
    \caption{The top panel shows the Galactic DWD confusion fit vs GW frequency for different binary evolution assumption variations (colors) with submodel F50 shown in dashed lines and submodel FZ shown in solid lines. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for submodel FZ to submodel F50 vs to number of DWDs orbiting in the LISA band for submodel F50 only. While both the height of the confusion foreground and number of LISA DWDs changes for each variation, the FZ submodels within each variation exhibit a constant reduction by a factor of two compared with the F50 submodels.}
    \label{fig:model_comp}
\end{figure}
